---
title: "Data Description"
author: "Author: Rajat Jain"
date: "Last Updated: `r Sys.Date()`"
time: "Time Spent: 2 Hrs"
output:
  pdf_document:
    toc: yes
  html_document:
    theme: lumen
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
setwd("/Users/rajatj/csx415/csx415-project/photographer_classifier")

# Project Template
library(ProjectTemplate)
# Load product usage data set from CSV file.
load.project()

# Scatter plots with ggplot
library(ggplot2)
# Classification Tree with rpart
library(rpart)
```

### Schema
We have first 7-day product usage data from Adobe photography plan users. Data is a CSV file containing `r nrow(usage.data)` rows. It has following columns:

* **member_guid:**   Customer Identifier.
* **class:**         Output Class - PHOTOGRAPHER or OTHER.
* **lr_cc_usage:**   # of times customer used Lightroom CC product in first 7-days.
* **lr_cl_usage:**   # of times customer used Lightroom Classic product in first 7-days.
* **lr_mo_usage:**   # of times customer used Lightroom Mobile product in first 7-days.
* **storage_usage:** # of times customer accessed Cloud Storage in first 7-days.
* **ps_usage:**      # of times customer used Photoshop product in first 7-days.
* **stock_usage:**   # of times customer searched for a Stock Image in first 7-days.


### Data Summary
```{r usage, echo=FALSE}
# Summarize Usage Data. First column is ID, ignore summarizing it.
summary(usage.data[,-1])
```


### Distribution of Class Labels
The bar chart below shows the distrubution of class labels in the input data (in absolute number of records).
```{r labels, message=FALSE, echo=FALSE}
label_distribution <- ggplot(data=usage.data, aes(x=class, fill=class)) +
  geom_bar(stat='count') + 
  labs( title="Distribution of Class Labels")
ggsave(file.path('../graphs', 'label_distribution.pdf'))

label_distribution
```

It contains **`r round(100 * nrow(usage.data[usage.data$class == "PHOTOGRAPHER",]) / nrow(usage.data), digits=1)`%** records classfied as "PHOTOGRAPHER" class and `r round(100 * nrow(usage.data[usage.data$class == "OTHER",]) / nrow(usage.data), digits=1)`% records in "OTHER" class.


### Binomial Test
Now we run Binomial Test on this data.
```{r binomial}
binom.test(nrow(usage.data[usage.data[,2] == "PHOTOGRAPHER",]), nrow(usage.data))
```