---
title: "Linear Model"
author: "Author: Rajat Jain"
date: "Last Updated: `r Sys.Date()`"
time: "Time Spent: 4 Hrs"
output:
  pdf_document:
    toc: yes
  html_document:
    theme: lumen
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
setwd("/Users/rajatj/csx415/csx415-project/photographer_classifier")

# Project Template
library(ProjectTemplate)
# Load product usage data set from CSV file.
load.project()

library(caret)
```

## Training & Test Data
```{r split, echo=FALSE}
smp_size <- floor(0.75 * nrow(usage.data))
# set the seed to make your partition reproductible
set.seed(123)
train_ind <- sample(seq_len(nrow(usage.data)), size = smp_size)
train <- usage.data[train_ind,]
test <- usage.data[-train_ind,]
```
We have split available usage data into training data (75% - `r nrow(train)` records) and test data(25% - `r nrow(test)` records).

Summary of Training data
```{r, echo=FALSE}
# Convert class label to 0|1.
train$class <- ifelse(train$class == "PHOTOGRAPHER", 1, 0)
train$class <- factor(train$class, levels = c(0, 1))

# First column is ID, ignore summarizing it.
summary(train[,-1])
```
Summary of Test data
```{r, echo=FALSE}
# First column is ID, ignore summarizing it.
summary(test[,-1])
```

## Training - Linear Model
Training a Logistic Regression model.
```{r linear}
#logistic regression model
model <- glm(class ~ lr_cc_usage + lr_cl_usage + storage_usage + ps_usage + stock_usage,
             data = train, family = binomial("logit"))
```

Summarize trained model.
```{r modelsummary}
summary(model)
```

## Prediction (Testing)
Once we have the model built on the training data, let's test in by predicting the output class on the test data.
```{r test}
pred <- predict(model, newdata=test, type = 'response')
pred.class <- ifelse(pred > 0.5, 'PHOTOGRAPHER', 'OTHER')
```


## Performance
Based on the measure defined in the FPS, we will use classification accuracy as our performance measure.

### Confusion Matrix
```{r confusion, echo=FALSE}
confusionMatrix(factor(pred.class), factor(test$class), positive="PHOTOGRAPHER")
```

### Accuracy
```{r accuracy, echo=FALSE}
accuracy <- round(mean(pred.class == test[ , 2])*100, digits=2)
performance <- ifelse(accuracy >= 70, 'Satisfactory', 'Not Satisfactory')
```

* Observed Accuracy : `r paste0(accuracy, "%")`
* Desired accuracy : 70%
* Performance is `r performance`.