---
title: "Tree Model"
author: 'Author: Rajat Jain'
date: 'Last Updated: `r Sys.Date()`'
output:
  pdf_document:
    toc: yes
  html_document:
    theme: lumen
    toc: yes
    toc_float: yes
time: 'Time Spent: 1 Hr'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
setwd("/Users/rajatj/csx415/csx415-project/photographer_classifier")

# Project Template
library(ProjectTemplate)
# Load product usage data set from CSV file.
load.project()

library(caret)

# Classification Tree with rpart
library(rpart)
```


## Training & Test Data
```{r split, echo=FALSE}
smp_size <- floor(0.75 * nrow(usage.data))
# set the seed to make your partition reproductible
set.seed(123)
train_ind <- sample(seq_len(nrow(usage.data)), size = smp_size)
train <- usage.data[train_ind,]
test <- usage.data[-train_ind,]
```
We have split available usage data into training data (75% - `r nrow(train)` records) and test data(25% - `r nrow(test)` records).

Summary of Training data
```{r, echo=FALSE}
# First column is ID, ignore summarizing it.
summary(train[,-1])
```
Summary of Test data
```{r, echo=FALSE}
# First column is ID, ignore summarizing it.
summary(test[,-1])
```


## Training - Tree Model
As the next step, we build a simple decision tree classifier model.
```{r tree}
# grow tree 
model <- rpart(class ~ lr_cc_usage + lr_cl_usage + storage_usage + ps_usage + stock_usage, 
             method="class", data=train)
```

Summarize trained model.
```{r modelsummary}
printcp(model) # display the results 
plotcp(model) # visualize cross-validation results 
summary(model) # detailed summary of splits
```

Plot tree.
```{r treeplot}
plot(model, uniform=TRUE, 
     main="Classification Tree for Photographers")
text(model, use.n=TRUE, all=TRUE, cex=.8)
```


## Prediction (Testing)
Once we have the model built on the training data, let's test in by predicting the output class on the test data.
```{r test}
pred <- predict(model, newdata=test, type="class")
```


## Performance
Based on the measure defined in the FPS, we will use classification accuracy as our performance measure.

### Confusion Matrix
```{r confusion, echo=FALSE}
confusionMatrix(factor(pred), factor(test$class), positive="PHOTOGRAPHER")
```

### Accuracy
```{r accuracy, echo=FALSE}
accuracy <- round(mean(pred == test[ , 2])*100, digits=2)
performance <- ifelse(accuracy >= 70, 'Satisfactory', 'Not Satisfactory')
```

* Observed Accuracy : `r paste0(accuracy, "%")`
* Desired accuracy : 70%
* Performance is `r performance`.