---
title: "Gradient Boosted Model"
author: 'Author: Rajat Jain'
date: 'Last Updated: `r Sys.Date()`'
output:
  pdf_document:
    toc: yes
  html_document:
    theme: lumen
    toc: yes
    toc_float: yes
time: 'Time Spent: 2 Hr'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
setwd("/Users/rajatj/csx415/csx415-project/photographer_classifier")

# Project Template
library(ProjectTemplate)
# Load product usage data set from CSV file.
load.project()

library(caret)
library(pROC)

# setup the doParallel
library(doParallel)
cl <- makeCluster(detectCores())
registerDoParallel(cl)
```


## Setting Training Control Params
Using 10-fold Cross Validation with 10 repeatitions.
```{r trainctrl}
ctrl <- trainControl(method="repeatedcv",
                     number=10,
                     repeats=10,
                     classProbs=TRUE,
                     savePredictions=TRUE,
                     allowParallel=TRUE)
set.seed(123)
```


## Training - Gradient Boosted Tree Model
Caret is Awesome!
```{r model}
fit <- train(class ~ lr_cc_usage + lr_cl_usage + storage_usage + ps_usage + stock_usage,
             data=usage.data, method = "gbm", trControl = ctrl)
```

Summarize trained model.
```{r modelsummary, echo=FALSE}
fit
```

```{r modelsave, echo=FALSE}
# Save model object for future use.
saveRDS(fit, "../pkgs/PhotographerModels/data/gbm.rds")
```


## Performance
Based on the measure defined in the FPS, we will use classification accuracy as our performance measure.

### Confusion Matrix
```{r confusion, echo=FALSE}
#confusionMatrix(factor(pred), factor(test$class), positive="PHOTOGRAPHER")
confusionMatrix(fit, positive="PHOTOGRAPHER")
```

### ROC Curve
```{r roc, echo=FALSE}
roc <- plot.roc(fit$pred$obs, fit$pred$PHOTOGRAPHER)
roc
```

### Accuracy
```{r accuracy, echo=FALSE}
accuracy <- round(100*max(fit$results$Accuracy), digits=2)
performance <- ifelse(accuracy >= 70, 'Satisfactory', 'Not Satisfactory')

kappa <- round(max(fit$results$Kappa), digits=2)
```

* Kohen's Kappa: `r kappa`
* Observed Accuracy : `r paste0(accuracy, "%")`
* Desired accuracy : 70%
* Performance is `r performance`.


```{r teardown, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
# stop the doParallel and release resources at the very end
stopCluster(cl)
```
